---
title: "Data Visualization Part 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Library

```{r}
library(tidyverse)
```

# Load Data

```{r}
country_data <- read_csv(file = "https://raw.githubusercontent.com/hadimaster65555/dataset_for_teaching/main/dataset/country_dataset/Country-data.csv")

indonesia_covid_data <- read_csv(file = "https://raw.githubusercontent.com/hadimaster65555/dataset_for_teaching/main/dataset/indocovid19/covid19_indonesia_datasets.csv")

turnover_data <- read_csv(file = "https://raw.githubusercontent.com/hadimaster65555/dataset_for_teaching/main/dataset/quebit_turnover_dataset/dataset%20V2.csv")

house_price <- read_csv(file = "https://raw.githubusercontent.com/hadimaster65555/dataset_for_teaching/main/dataset/house-prices-advanced-regression-techniques/train.csv")

berkeley <- read_csv(file = "https://raw.githubusercontent.com/Murillo/Data-Science-Udacity/master/Intro%20Data%20Science/1.%20Introduction/Simpson-Paradox/Berkeley.csv")
```

# ggplot2 Basic Structure

```{r}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width
  )) +
  # third layer: geometric form
  geom_point()
```

## Multiple Way to Plot

**Cara 1**

```{r}
# layer 1: data
raw_data %>% 
  # membuat plot kosong
  ggplot() + 
  # layer 2: aesthetic untuk data
  # variabel x = mpg
  # variabel y = disp
  aes(x = mpg, y = disp) +
  # layer 3: geometry geom_point
  geom_point()
```

**Cara 2**

```{r}
# layer 1: data
raw_data %>% 
  # layer 2: aesthetic untuk data
  # variabel x = mpg
  # variabel y = disp
  ggplot(aes(x = mpg, y = disp)) + 
  # layer 3: geometry geom_point
  geom_point()
```

**Cara 3**

```{r}
ggplot(
  # layer 1: data
  data = raw_data,
  # layer 2: aesthetic
  # variabel x = mpg
  # variabel y = disp
  mapping = aes(x = mpg, y = disp)) + 
  # layer 3: geometry geom_point
  geom_point()
```

# aes() and geom_*() Function

## Single Geometries

**Without Lables**

```{r}
# seeding
set.seed(1000)

# from country data
country_data %>% 
  sample_n(size = 50) %>% 
  # add aesthetic:, y = child mortality
  ggplot(
    aes(
      # x = country income
      x = income, 
      # y = child mortality
      y = child_mort, 
      # colour = life expectacy
      colour = life_expec,
      # size = inflation rate
      size = inflation
    )
  ) + 
  # add geometries: point
  geom_point()
```

**With Text**

```{r}
# seeding
set.seed(1000)

# from country data
country_data %>% 
  sample_n(size = 50) %>% 
  # add aesthetic:, y = child mortality
  ggplot(
    aes(
      # x = country income
      x = income, 
      # y = child mortality
      y = child_mort, 
      # colour = life expectacy
      colour = life_expec,
      # size = inflation rate
      size = inflation,
      # label = coutry name
      label = country
    )
  ) + 
  # add geometries: point
  geom_point() + 
  # add text
  geom_text()
```

**With Label**

```{r}
# seeding
set.seed(1000)

# from country data
country_data %>% 
  sample_n(size = 50) %>% 
  # add aesthetic:, y = child mortality
  ggplot(
    aes(
      # x = country income
      x = income, 
      # y = child mortality
      y = child_mort, 
      # colour = life expectacy
      colour = life_expec,
      # size = inflation rate
      size = inflation,
      # label = coutry name
      label = country
    )
  ) + 
  # add geometries: point
  geom_point() + 
  # add label
  geom_label()
```

**Barplot**

```{r}
# layer 1: turnover data
turnover_data %>% 
  # layer 2: x = gender
  ggplot(aes(x = gender)) +
  # layer 3: Barplot geometry
  geom_bar()
```

**Column Plot**

```{r}
# layer 1: turnover_data
turnover_data %>% 
  # count gender
  count(gender) %>%
  # layer 2: x = gender, y = n, fill = gender
  ggplot(aes(x = gender, y = n, fill = gender)) +
  # layer 3: Column geometry
  geom_col()
```

**Boxplot**

```{r}
# layer 1: Turnover data
turnover_data %>% 
  # layer 2: x = salary
  ggplot(aes(x = salary)) +
  # layer 3: Boxplot geometry
  geom_boxplot()
```

**Violin Plot**

```{r}
# layer 1: Turnover data
turnover_data %>% 
  # layer 2: x = salary
  ggplot(aes(x = "Salary", y = salary)) +
  # layer 3: Violin geometry
  geom_violin()
```


**Density Plot**

```{r}
# layer 1: Turnover data
turnover_data %>% 
  # layer 2: x = salary
  ggplot(aes(x = salary)) +
  # layer 3: Histogram geometry
  geom_histogram(bins = 15)
```

**Density Plot**

```{r}
# layer 1: Turnover data
turnover_data %>% 
  # layer 2: x = salary
  ggplot(aes(x = salary)) +
  # layer 3: Histogram geometry
  geom_density()
```

**Line Plot**

```{r}
# layer 1: indonesia COVID-19 data
indonesia_covid_data %>% 
  # layer 2: x = day, y = new cases by day
  ggplot(aes(x = day, y = new_cases_by_day)) +
  # layer 3a: Line geometry
  geom_line(color = "blue") + 
  # layer 3a: Line geometry
  geom_line(aes(y = death_by_day), color = "red")
```

**Area Plot**

```{r}
# layer 1: indonesia COVID-19 data
indonesia_covid_data %>% 
  # layer 2: x = day, y = new cases by day
  ggplot(aes(x = day, y = cumulative_death)) +
  # layer 3: Area geometry
  geom_area()
```

**Dot Plot**

```{r}
# layer 1: country data
country_data %>% 
  # layer 2: x = child mortality
  ggplot(aes(x = child_mort)) +
  # layer 3: Dotplot geometry
  geom_dotplot()
```

**Jitter Plot**

```{r}
# layer 1: turnover_data
turnover_data %>% 
  # layer 2: x = gender, y = salary
  ggplot(aes(x = gender, y = salary)) +
  # layer 3: Jitter geometry
  geom_jitter(width = 0.1)
```

**Heatmap/Tile Plot**

```{r}
# layer 1: turnover_data
turnover_data %>%
  group_by(education_level, position) %>% 
  summarise(mean_salary = mean(salary)) %>% 
  ungroup() %>% 
  # layer 2: aesthetic
  ggplot(aes(
    # education level
    x = education_level,
    # position
    y = position, 
    # mean_salary
    fill = mean_salary
  )) + 
  # layer 3: Tile Geometries
  geom_tile()
```

## Grouping Geometries

**Groupped Scatter Plot**

```{r}
# layer 1: turnover_data
turnover_data %>% 
  # layer 2: x = experience, y = salary, fill = level
  ggplot(aes(x = experience, y = salary, col = factor(level))) +
  # layer 3: Point geometry
  geom_point()
```

**Multiple Box Plot**

```{r}
# layer 1: turnover_data
turnover_data %>% 
  # layer 2: x = education level, y = salary, fill = education level
  ggplot(aes(x = education_level, y = salary, fill = education_level)) +
  # layer 3: Boxplot geometry
  geom_boxplot()
```

**Multiple Jitter Plot**

```{r}
# layer 1: turnover_data
turnover_data %>% 
  # layer 2: x = education level, y = salary, fill = education level
  ggplot(aes(x = education_level, y = salary, col = education_level)) +
  # layer 3: Column geometry
  geom_jitter(width = 0.1)
```

**Boxplot with Jitter**

```{r}
# layer 1: turnover_data
turnover_data %>% 
  # layer 2: x = gender, y = salary
  ggplot(aes(x = gender, y = salary)) +
  # layer 3a: Boxplot geometry
  geom_boxplot() + 
  # layer 3b: Jitter geometry
  geom_jitter(
    # add fill to gender
    aes(col = gender),
    # jitter width
    width = 0.1, 
    # jitter opacity
    alpha = 0.3
  )
```

**Multiple Line Plot**

```{r}
indonesia_covid_data %>%
  select(day, new_cases_by_day, death_by_day) %>% 
  pivot_longer(!day) %>% 
  ggplot(aes(x = day, y = value, col = name)) + 
  geom_line()
```

**Multiple Area Plot**

```{r}
indonesia_covid_data %>%
  select(day, new_cases_by_day, death_by_day) %>% 
  pivot_longer(!day) %>% 
  ggplot(aes(x = day, y = value, fill = name)) + 
  geom_area(position = "stack", alpha = 0.5)
```

**Grouped Dot Plot**

```{r}
set.seed(1000)

# layer 1: turnover_data
turnover_data %>% 
  sample_n(1000) %>% 
  # layer 2: x = gender, y = salary, fill = gender, col = gender
  ggplot(aes(x = gender, y = salary, fill = gender, col = gender)) +
  # layer 3: Column geometry
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 0.2)
```

**Grouped Histogram**

```{r}
# layer 1: turnover_data
turnover_data %>% 
  # layer 2: x = salary, fill = gender
  ggplot(aes(x = salary, fill = gender)) +
  # layer 3: Histogram geometry
  geom_histogram(bins = 15, alpha = 0.6, position = "stack")
```

**Grouped Column Plot**

```{r}
# Layer 1: turnover_data
turnover_data %>% 
  group_by(gender, status) %>% 
  count() %>% 
  ungroup() %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Status
    x = status, 
    # n
    y = n,
    # Gender
    fill = gender
  )) + 
  # Layer 3: Column geometry
  geom_col(position = "dodge")
```

**Stacker Column Plot**

```{r}
# Layer 1: turnover_data
turnover_data %>% 
  group_by(gender, status) %>% 
  count() %>% 
  ungroup() %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Status
    x = status, 
    # n
    y = n,
    # Gender
    fill = gender
  )) + 
  # Layer 3: Column geometry
  geom_col(position = "stack")
```

**Proportional Stacked Column Plot**

```{r}
# Layer 1: turnover_data
turnover_data %>% 
  group_by(gender, status) %>% 
  count() %>% 
  ungroup() %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Status
    x = status, 
    # n
    y = n,
    # Gender
    fill = gender
  )) + 
  # Layer 3: Column geometry
  geom_col(position = "fill")
```


**Smooth Line**

```{r}
# layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # House Sale Price
    y = SalePrice
  )) + 
  # Layer 3: Smooth geometry
  geom_smooth()
```

Note:

- method parameter: parameter used for smoothing method:
  - ```auto```, use loess method
  - ```lm```, use linear regression method
  - ```glm```, use generalized linear model
  - ```gam```, use generalized additive model
  - ```loess```, use loess method
- se parameter: use standard error or not

```{r}
# layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # House Sale Price
    y = SalePrice
  )) + 
  # Layer 3: Smooth geometry with linear model
  geom_smooth(method = "lm")
```

```{r}
# layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # House Sale Price
    y = SalePrice
  )) + 
  # Layer 3: Smooth geometry with GLM method
  geom_smooth(method = "glm")
```

```{r}
# layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # House Sale Price
    y = SalePrice
  )) + 
  # Layer 3: Smooth geometry with GAM method without standard error
  geom_smooth(method = "gam", se = F)
```

```{r}
# layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # House Sale Price
    y = SalePrice
  )) + 
  # Layer 3a: Point geometry
  geom_point() +
  # Layer 3b: Smooth geometry with GLM method
  geom_smooth(method = "glm")
```

```{r}
# layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # House Sale Price
    y = SalePrice
  )) + 
  # Layer 3a: Point geometry
  geom_point() +
  # Layer 3b: Smooth geometry with GAM method without standard error
  geom_smooth(method = "gam")
```

```{r}
# layer 1: House Price
indonesia_covid_data %>%
  # layer 2: Aesthetic
  ggplot(aes(
    # Day
    x = day, 
    # New Cases by Day
    y = new_cases_by_day
  )) +
  # layer 3a: Line geometry
  geom_line() + 
  # layer 3b: Smooth geometry
  geom_smooth()
```

# theme_*() Function

**No Theme**

```{r fig.width=5}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() 
```

**Gray Theme**

```{r fig.width=5}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() + 
  # add gray theme
  theme_gray()
```

**Grey Theme**

```{r fig.width=5}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() + 
  # add grey theme
  theme_grey()
```

**Black and White Theme**

```{r fig.width=5}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() + 
  # add black and white theme
  theme_bw()
```

**Linedraw Theme**

```{r fig.width=5}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() + 
  # add grey theme
  theme_linedraw()
```

**Light Theme**

```{r fig.width=5}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() + 
  # add light theme
  theme_light()
```

**Dark Theme**

```{r fig.width=5}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() + 
  # add dark theme
  theme_dark()
```

**Minimal Theme**

```{r fig.width=5}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() + 
  # add minimal theme
  theme_minimal()
```

**Classic Theme**

```{r fig.width=5}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() + 
  # add classic theme
  theme_classic()
```

**Void Theme**

```{r fig.width=5}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() + 
  # add void theme
  theme_void()
```

**Test Theme**

```{r fig.width=5}
# first layer: data
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() + 
  # add test theme
  theme_test()
```

# labs() Function

```{r}
iris %>% 
  # second layer: aesthetics
  ggplot(aes(
    x = Sepal.Length, 
    y = Sepal.Width, 
    color = Species
  )) +
  # third layer: geometric form
  geom_point() + 
  # add grey theme
  theme_minimal() + 
  labs(
    # add title
    title = "Iris Plot",
    # add subtitle
    subtitle = "Based on Fisher Dataset",
    # change x label
    x = "Sepal Length",
    # change y label
    y = "Sepal Width",
    # change caption
    caption = "Plot made by Hadimaster",
    # change tag
    tag = "Clustering Example"
  )
```

# On Plot Axis and Scales

## scale_(aes variable)_(type/transform) Function

**scale_x_continous()**

*Before*

```{r}
# Layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # House Sale Price
    y = SalePrice, 
    # Electrical Type
    color = Electrical
  )) + 
  # Layer 3: Point geometry
  geom_point() +
  # Layer 4: Minimal theme
  theme_minimal()
```

*After*

```{r}
# Layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # House Sale Price
    y = SalePrice, 
    # Electrical Type
    color = Electrical
  )) + 
  # Layer 3: Point geometry
  geom_point() +
  # Layer 4: Minimal theme
  theme_minimal() +
  # Layer 5: Change y continuous scale labels
  scale_y_continuous(labels = scales::number)
```

*Before*

```{r}
# Layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # Parking Lot Area
    y = LotArea, 
    # Sale Price
    color = SalePrice
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal()
```

*After*

```{r}
# Layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # Parking Lot Area
    y = LotArea, 
    # Sale Price
    color = SalePrice
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal() +
  # Layer 5: Change color continuous scale labels
  scale_color_continuous(labels = scales::number)
```

*Before*

```{r}
# Layer 1: House price
house_price %>% 
  # Remove NA values in Electrical
  filter(!is.na(Electrical)) %>% 
  # Group by Electrical
  group_by(Electrical) %>%
  # Summarise data
  summarise(
    # find mean of Sale Price
    TotalSalePrice = sum(SalePrice)
  ) %>% 
  ungroup() %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Electrical
    x = reorder(Electrical, -TotalSalePrice), 
    # Total Sale Price
    y = TotalSalePrice,
    # Total Sale Price
    fill = TotalSalePrice
  )) + 
  # Layer 3: Column Plot
  geom_col() + 
  # Layer 4: Labels
  labs(
    # Change x label to Electrical
    x = "Electrical",
    # Change y label to Total Sale Price
    y = "Total Sale Price",
    # Change legend title to Total Sale Price
    fill = "Total Sale Price"
  )
```

*After*

```{r}
# Layer 1: House price
house_price %>% 
  # Remove NA values in Electrical
  filter(!is.na(Electrical)) %>% 
  # Group by Electrical
  group_by(Electrical) %>%
  # Summarise data
  summarise(
    # find mean of Sale Price
    TotalSalePrice = sum(SalePrice)
  ) %>% 
  ungroup() %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Electrical
    x = reorder(Electrical, -TotalSalePrice), 
    # Total Sale Price
    y = TotalSalePrice,
    # Total Sale Price
    fill = TotalSalePrice
  )) + 
  # Layer 3: Column Plot
  geom_col() + 
  # Layer 4: Labels
  labs(
    # Change x label to Electrical
    x = "Electrical",
    # Change y label to Total Sale Price
    y = "Total Sale Price",
    # Change legend title to Total Sale Price
    fill = "Total Sale Price"
  ) +
  # Layer 5a: Change fill labels to number
  scale_fill_continuous(labels = scales::number) + 
  # Layer 5b: Change y continous labels to number
  scale_y_continuous(labels = scales::number)
```

**scale_x_log10() and scale_y_log10()**

*Before*

```{r}
# Layer 1: House price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF
  )) + 
  # Layer 3: Histogram geometry
  geom_histogram()
```

*After*

```{r}
# Layer 1: House price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF
  )) + 
  # Layer 3: Histogram geometry
  geom_histogram() +
  # Layer 4: Transform x variable with log10
  scale_x_log10()
```

*Before*

```{r}
# Layer 1: House price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # Sale Price
    y = SalePrice,
    # Electrical
    color = Electrical
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal()
```

*After*

```{r}
# Layer 1: House price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # Sale Price
    y = SalePrice,
    # Electrical
    color = Electrical
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal() + 
  # Layer 5a: Transform x variable with log10
  scale_x_log10() +
  # Layer 5b: Transform y variable with log10
  scale_y_log10()
```

*Before*

```{r}
# Layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Squre Feet
    x = TotalBsmtSF, 
    # Garage Area
    y = GarageArea,
    # Sale Price
    color = SalePrice
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal()
```

*After*

```{r}
# Layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Squre Feet
    x = TotalBsmtSF, 
    # Garage Area
    y = GarageArea,
    # Sale Price
    color = SalePrice
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal() +
  # Layer 5: Change color to viridis binned
  scale_colour_viridis_b(labels = scales::number)
```

```{r}
# Layer 1: House Price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Squre Feet
    x = TotalBsmtSF, 
    # Garage Area
    y = GarageArea,
    # Sale Price
    color = SalePrice
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal() +
  # Layer 5: Change color to viridis continous
  scale_colour_viridis_c(labels = scales::number)
```

## coord_*() Function

**coord_cartesian()**

*Before*

```{r}
# Layer 1: House price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Squre Feet
    x = TotalBsmtSF, 
    # Garage Area
    y = GarageArea,
    # Sale Price
    color = SalePrice
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal()
```

*After*

```{r}
# Layer 1: House price
house_price %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Squre Feet
    x = TotalBsmtSF, 
    # Garage Area
    y = GarageArea,
    # Sale Price
    color = SalePrice
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal() +
  # Layer 5: Use Cartesian coordinate
  coord_cartesian(
    # with y around 100-500
    ylim = c(100, 500), 
    # with x around 0-2000
    xlim = c(0, 2000)
  )
```

**coord_flip()**

*Before*

```{r}
# Layer 1: turnover_data
turnover_data %>% 
  # count gender
  count(gender) %>%
  # Layer 2: Aesthetics
  ggplot(aes(
    # Gender
    x = gender, 
    # n
    y = n,
    # Gender
    fill = gender
  )) +
  # Layer 3: Column geometry
  geom_col() 
```

```{r}
# Layer 1: turnover_data
turnover_data %>% 
  # count gender
  count(position) %>%
  # Layer 2: Aesthetics
  ggplot(aes(
    # Position
    x = position,
    # n
    y = n,
    # Position
    fill = position
  )) +
  # Layer 3: Column geometry
  geom_col() +
  # Layer 4: Flip coordinate
  coord_flip()
```

**coord_polar()**

*Before*

```{r}
# layer 1: turnover_data
turnover_data %>% 
  # count gender
  count(gender) %>%
  # layer 2: x = gender, y = n, fill = gender
  ggplot(aes(
    # Blank
    x = "",
    # n
    y = n,
    # Gender
    fill = gender
  )) +
  # layer 3: Column geometry
  geom_col() 
```

*After*

```{r}
# layer 1: turnover_data
turnover_data %>% 
  # count gender
  count(gender) %>%
  # layer 2: x = gender, y = n, fill = gender
  ggplot(aes(x = "", y = n, fill = gender)) +
  # layer 3: Column geometry
  geom_col() +
  # Layer 4: Change coordinate to polar
  coord_polar(
    # y-axis as reference
    theta = "y", 
    # start from 0
    start = 0
  ) + 
  # Layer 5: Void theme
  theme_void()
```

# Break Up Plot using facet_*() Function

**Before Faceting**

```{r}
# Layer 1: House price
house_price %>% 
  # Filter out NA values on Electrical
  filter(!is.na(Electrical)) %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # Sale Price
    y = SalePrice, 
    # Electrical
    color = Electrical
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal()
```

**Facet Grid**

```{r}
# Layer 1: House price
house_price %>% 
  # Filter out NA values on Electrical
  filter(!is.na(Electrical)) %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # Sale Price
    y = SalePrice, 
    # Electrical
    color = Electrical
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal() +
  # Layer 5: Facet with grid
  facet_grid(Electrical ~ .)
```

```{r}
# Layer 1: House price
house_price %>% 
  # Filter out NA values on Electrical
  filter(!is.na(Electrical)) %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # Sale Price
    y = SalePrice, 
    # Electrical
    color = Electrical
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal() +
  # Layer 5: Facet with wrap
  facet_wrap(Electrical ~ .)
```

```{r}
# Layer 1: House price
house_price %>% 
  # Filter out NA values on Electrical
  filter(!is.na(Electrical)) %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # Sale Price
    y = SalePrice, 
    # Electrical
    color = Electrical
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal() +
  # Layer 5: Facet with wrap
  facet_wrap(
    Electrical ~ .,
    # Use 2 column
    ncol = 2,
    # Use free scales
    scales = "free"
  )
```

```{r}
# Layer 1: House price
house_price %>% 
  # Filter out NA values on Electrical
  filter(!is.na(Electrical)) %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Total Basement Square Feet
    x = TotalBsmtSF, 
    # Sale Price
    y = SalePrice, 
    # Electrical
    color = Electrical
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Minimal theme
  theme_minimal() +
  # Layer 5: Facet with wrap
  facet_grid(
    Electrical ~ .,
    # Use free scales
    scales = "free",
    # Use free space
    space = "free"
  )
```

```{r}
# Layer 1: turnover_data
turnover_data %>% 
  group_by(gender, status) %>% 
  count() %>% 
  ungroup() %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Status
    x = status, 
    # n
    y = n,
    # Gender
    fill = gender
  )) + 
  # Layer 3: Column geometry
  geom_col(position = "dodge") + 
  # Layer 4: Faceting
  facet_wrap(
    .~status,
    # Change scale x to free
    scales = "free"
  )

```

