---
title: "Data Visualization Part 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(patchwork)
library(ggrepel)
library(echarts4r)
library(leaflet)
```


```{r}
# geolocation data
geolocation_data <- read_delim(file = "https://raw.githubusercontent.com/hadimaster65555/dataset_for_teaching/main/dataset/sulawesi_hotspot_data/File%20Hotspot%20Pulau%20Sulawesi%20-%20(2016-2018).csv", delim = ";")

# country data
country_data <- read_csv(file = "https://raw.githubusercontent.com/hadimaster65555/dataset_for_teaching/main/dataset/country_dataset/Country-data.csv")

# turnover data
turnover_data <- read_csv(file = "https://raw.githubusercontent.com/hadimaster65555/dataset_for_teaching/main/dataset/quebit_turnover_dataset/dataset%20V2.csv")

# Indonesia COVID19 data
indocovid_data <- read_csv(file = "https://raw.githubusercontent.com/hadimaster65555/dataset_for_teaching/main/dataset/indocovid19/covid19_indonesia_datasets.csv")

# amazon stock data
amazon_data <- read_csv(file = "https://raw.githubusercontent.com/yumoxu/stocknet-dataset/master/price/raw/AMZN.csv")

# michigan county
michigan_county <- map_data(map = "county", "michigan")

# indonesia map
indonesia_map <- map_data(map = "world", region = "Indonesia")
```

# Customer Theme using theme() Function 

*Before*

```{r}
# Layer 1: Country data
country_data %>% 
  # Layer 2: Aesthetics
  ggplot(aes(
    # Income
    x = income, 
    # Child Mortality
    y = child_mort, 
    # Inflation
    size = inflation
  )) + 
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Change or add labels
  labs(
    title = "Child Morlatity vs Country Income & Inflation",
    x = "Income",
    y = "Child Mortality",
    size = "Inflation"
  ) -> plot_1
```

```{r}
# see plot 1
plot_1
```

## Customize Plot Elements

**plot.background**

```{r}
# from plot_1
plot_1 + 
  # Customize theme
  theme(
    # customize plot background color with light blue
    plot.background = element_rect(fill = "lightblue")
  )
```

**plot.margin**

```{r}
# from plot_1
plot_1 + 
  # Customize theme
  theme(
    # add margin from top = 100 and bottom = 100
    plot.margin = margin(t = 100, r = 0, b = 100, l = 0)
  )
```

**plot.title**

```{r}
# from plot_1
plot_1 + 
  # Customize theme
  theme(
    # change font to bold and font family to OpenDyslexic 
    # (if this font exist in your MS Word or LibreOffice)
    plot.title = element_text(face = "italic", family = "OpenDyslexic")
  )
```

## Customize Axis Elements

**axis.line**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change axis line color to red with size 2
    axis.line = element_line(colour = "red", size = 2)
  )
```

**axis.text**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change all axis text color to blue and bold
    axis.text = element_text(color = "blue", face = "bold")
  )
```

**axis.text.x and axis.text.y**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change only x-axis text color to blue
    axis.text.x = element_text(colour = "blue"),
    # change only y-axis text color to green
    axis.text.y = element_text(color = "green")
  )
```

**axis.title**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change all axis title text color to blue and bold
    axis.title = element_text(color = "blue", face = "bold")
  )
```

**axis.title.x and axis.title.y**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change only x-axis title text color to blue
    axis.title.x = element_text(color = "blue"),
    # change only y-axis title text color to green
    axis.title.y = element_text(color = "green")
  )
```

## Customize Legend Elements

**legend.background**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change legend background color to grey
    legend.background = element_rect(fill = "grey")
  )
```

**legend.key**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change legend key background color to grey
    legend.key = element_rect(fill = "grey")
  )
```

**legend.key.size**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change legend key size to 0.1 cm
    legend.key.size = unit(0.1, "cm")
  )
```

**legend.margin**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change legend margin with bottom = 200 pt
    legend.margin = margin(t = 0, r = 0, b = 200, l = 0)
  )
```

**legend.text**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change legend text with bold and size = 10, change color to blue
    legend.text = element_text(face = "bold", size = 10, color = "blue")
  )
```

**legend.title**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change legend title text with bold, change color to red
    legend.title = element_text(face = "bold", color = "red")
  )
```

## Customize Panel Elements

**panel.background**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change panel background to lightblue
    panel.background = element_rect(fill = "lightblue")
  )
```

**panel.grid**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change panel grid color to black
    panel.grid = element_line(colour = "black")
  )
```

**panel.grid.major**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change major grid color to blue
    panel.grid.major = element_line(color = "blue")
  )
```

**panel.grid.minor**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change panel minor grid color to red and size to 1
    panel.grid.minor = element_line(color = "red", size = 1)
  )
```

**aspect.ratio**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change aspect ratio to 1:1
    aspect.ratio = 1
  )
```

**Use Multiple Theme**

```{r}
# from plot_1
plot_1 +
  # customize theme
  theme(
    # change plot title
    plot.title = element_text(face = "bold", size = 12, margin = margin(r = 10)),
    # Change legend background
    legend.background = element_rect(fill = "white", colour = "gray"),
    # axis tick
    axis.ticks = element_line(colour = "black", size = 1),
    # major panel grid
    panel.grid.major = element_line(colour = "black", size = 0.05),
    # minor panel grid
    panel.grid.minor = element_line(colour = "black", size = 0.05),
    # axis line
    axis.line = element_line(colour = "red", size = 0.2),
    # axis text
    axis.text = element_text(face = "bold", size = 12),
    # x-axis text
    axis.title.x = element_text(face = "bold", size = 10),
    # y-axis text
    axis.title.y = element_text(face = "bold", size = 10),
    # panel background
    plot.background = element_rect(fill = "grey80"),
    # panel background
    panel.background = element_rect(fill = "linen"),
    # legend text
    legend.title = element_text(face = "bold")
  )
```

# Visualize Map using ggplot2

**Inspect Data**

```{r}
# from geolocation_data
geolocation_data %>% 
  # check data structure
  glimpse()
```

**Point-Type**

```{r}
# Layer 1: Geolocation data
geolocation_data %>% 
  # Layer 2: Aesthetics
  ggplot(aes(x = longitude, y = latitude)) +
  # Layer 3: Point geometry
  geom_point() + 
  # Layer 4: Change catersian to map coordinate
  coord_quickmap() + 
  # Layer 5: Minimal theme
  theme_minimal()
```

```{r}
# Layer 1: Geolocation data
geolocation_data %>% 
  # Layer 2: Aesthetics
  ggplot(aes(x = longitude, y = latitude)) +
  # Layer 3: Point geometry
  geom_point(size = 2) + 
  # Layer 4: Change catersian to map coordinate
  coord_quickmap() + 
  # Layer 5: Minimal theme
  theme_minimal()
```

**Polygon-Type**

```{r}
# Layer 1: Geolocation data
michigan_county %>% 
  # Layer 2: Aesthetics
  ggplot(aes(x = long, y = lat, group = group)) +
  # Layer 3: Point geometry
  geom_polygon(fill = "white", color = "black") + 
  # Layer 4: Change catersian to map coordinate
  coord_quickmap() + 
  # Layer 5: Minimal theme
  theme_minimal()
```

```{r}
# Layer 1: Geolocation data
indonesia_map %>% 
  # Layer 2: Aesthetics
  ggplot(aes(x = long, y = lat, group = group)) +
  # Layer 3: Point geometry
  geom_polygon(fill = "white", color = "black") + 
  # Layer 4: Change catersian to map coordinate
  coord_quickmap() + 
  # Layer 5: Minimal theme
  theme_minimal()
```

# Arrange Plot Using Patchwork

```{r}
# Layer 1: Turnover data
turnover_data %>% 
  # count gender
  count(gender) %>%
  # Layer 2: Aesthetics
  ggplot(aes(x = gender, y = n, fill = gender)) + 
  # Layer 3: Column geometry
  geom_col() +
  # Layer 4: Eliminate legend
  theme(legend.position = "none") -> p1

# Layer 1: Turnover data
turnover_data %>% 
  # Layer 2: Aesthetics
  ggplot(aes(x = position, y = salary, fill = position)) + 
  # Layer 3: Violin Geometry
  geom_violin() + 
  # Layer 4: Flip Coordinate
  coord_flip() +
  # Layer 5: Eliminate legend
  theme(legend.position = "none") -> p2

# Layer 1: Turnover data
turnover_data %>% 
  # Layer 2: Aesthetics
  ggplot(aes(x = senority, y = salary, col = salary)) + 
  # Layer 3: Point Geometry
  geom_point() -> p3

# Layer 1: Turnover data
turnover_data %>%
  count(department) %>% 
  # Layer 2: Aesthetics
  ggplot(aes(x = department, y = n, fill = department)) + 
  # Layer 3: Column Geometries
  geom_col() +
  # Layer 4: Remove legend
  theme(legend.position = "none") + 
  # Layer 5: Flip coordinate
  coord_flip() -> p4
```

## Horizontal Arrangemenr by Using + Operator

```{r}
# add p1 and p2 horizontally
p1 + p2
```

```{r}
# add p1, p2 and p3 horizontally
p1 + p2 + p3
```

## Vertical Arrangement by Using / Operator

```{r}
# add p1 and p2 vertically
p1 / p2
```

```{r}
# add p1, p2 and p3 vertivally
p1 / p2 / p3
```

## Bind Vertical and Horizontal Arrangement

```{r}
# add p1 horizontally while p2 and p3 vertically
p1 + p2 / p3
```

```{r}
# add p2 vertically while p1 and p3 horizontally
p2 / (p1 + p3)
```

## Bind Plots Using wrap_plot()

```{r}
# wrap all plot
wrap_plots(p1, p2, p3, p4)
```

## Add Space With plot_spacer()

**Without Plot Spacer**

```{r}
p1 + p2
```

**With Plot Spacer**

```{r}
# add p1 and p2 with spacer in between
p1 + plot_spacer() + p2
```

## Controlling Grid by Using plot_layout()

**Without plot_layout**

```{r}
p1 + p2 + p3 + p4
```

**Using plot_layout() with grid columns = 3**

```{r}
p1 + p2 + p4 + p3 + plot_layout(ncol = 3)
```

## Insert Plot Inside Another Plot With inset_element()

```{r}
p1 + inset_element(p3, left = 0.01, bottom = 0.6, right = 0.5, top = 1)
```


# Repel Text using ggrepel

**Without ggrepel**

```{r}
set.seed(1000)

# layer 1: Country data
country_data %>% 
  sample_n(size = 30) %>%
  # Layer 2: Aesthetics
  ggplot(aes(x = income, y = child_mort, label = country)) +
  # Layer 3: Point Geometry
  geom_point() + 
  # Layer 4: Text Geometry (Add text)
  geom_text() + 
  # Layer 5: Minimal theme
  theme_minimal()
```

**With geom_text_repel()**

```{r}
set.seed(1000)

# layer 1: Country data
country_data %>% 
  sample_n(size = 30) %>%
  # Layer 2: Aesthetics
  ggplot(aes(x = income, y = child_mort, label = country)) +
  # Layer 3: Point Geometry
  geom_point() + 
  # Layer 4: Text Geometry and Repel them from point (Add text)
  geom_text_repel() + 
  # Layer 5: Minimal theme
  theme_minimal()
```

```{r}
set.seed(1000)

# layer 1: Country data
country_data %>% 
  sample_n(size = 30) %>%
  # Layer 2: Aesthetics
  ggplot(aes(x = income, y = child_mort, label = country)) +
  # Layer 3: Point Geometry
  geom_point() + 
  # Layer 4: Label Geometry and Repel them from point (Add label)
  geom_label_repel() + 
  # Layer 5: Minimal theme
  theme_minimal()
```

# Interactive Plot Using echarts4r

## Basic Syntax

```
# from data
data %>% 
  # create echarts object with x vector
  e_charts(x_vector) %>% 
  # create chart with y vector
  e_<chart_name>(y_vector)
```

## Scatter Plot with e_scatter()

```{r}
# from country data
country_data %>% 
  # call echarts object with x vector
  e_charts(income) %>% 
  # call e_scatter with chiild mortality as y vector
  e_scatter(child_mort, size = inflation)
```

## Barplot with e_bar

```{r}
# from turnover data
turnover_data %>% 
  # count
  count(gender) %>%
  # call echarts object with gender as x axis
  e_charts(gender) %>% 
  # create bar chart with n as y axis and rename it as total employee
  e_bar(n, name = "Total Employee")
```

```{r}
# from turnover data
turnover_data %>% 
  # count
  count(position) %>% 
  # sort
  arrange(n) %>% 
  # call echarts object with position as x axis
  e_charts(position) %>% 
  # create bar chart with n as y axis and rename it as total employee
  e_bar(n, name = "Total Employee") %>% 
  # flip coordinates
  e_flip_coords() %>% 
  # add tooltip with item as a trigger
  e_tooltip("item")
```

## Pie Chart with e_pie

**Basic Pie Chart**

```{r}
# from turnover data
turnover_data %>% 
  # count
  count(gender) %>%
  # call echarts object with gender as x axis
  e_charts(gender) %>% 
  # create pie chart with n as y axis and rename it as total employee
  e_pie(n, name = "Total Employee") %>% 
  # add tooltip with item as trigger
  e_tooltip("item")
```

**Donut Chart**

```{r}
# from turnover data
turnover_data %>% 
  # count
  count(gender) %>%
  # call echarts object with gender as x axis
  e_charts(gender) %>% 
  # create pie chart with n as y axis and rename it as total employee
  e_pie(n, name = "Total Employee", radius = c("50%", "70%")) %>% 
  # add tooltip with item as trigger
  e_tooltip("item")
```

**Rosetype**

```{r}
# from turnover data
turnover_data %>% 
  # count
  count(gender) %>%
  # call echarts object with gender as x axis
  e_charts(gender) %>% 
  # create pie chart with n as y axis and rename it as total employee
  e_pie(n, name = "Total Employee", roseType = "radius") %>% 
  # add tooltip with item as trigger
  e_tooltip("item")
```

## Line Chart with e_line

```{r}
# from indocovid data
indocovid_data %>% 
  # add e_charts object with day as x-axis
  e_charts(day) %>%
  # add line chart with new_cases_by_day as 1st y-axis
  e_line(new_cases_by_day, smooth = T) %>% 
  # add line chart with in_care_by_day as 2nd y-axis
  e_line(in_care_by_day, smooth = T) %>% 
  # add line chart with death_by_day as 3rd y-axis
  e_line(death_by_day, smooth = T) %>% 
  # add tooltip with axis as trigger
  e_tooltip("axis")
```

```{r}
# from indocovid data
indocovid_data %>% 
  # add e_charts object with day as x-axis
  e_charts(day) %>%
  # add line chart with new_cases_by_day as 1st y-axis
  e_line(new_cases_by_day, smooth = T) %>% 
  # add line chart with in_care_by_day as 2nd y-axis and on another index
  e_line(in_care_by_day, smooth = T, x_index = 1, y_index = 1) %>%
  # create grid with width around 35% of canvas
  e_grid(width = "35%") %>%
  # create grid with width around 35% of canvas and 55% from left
  e_grid(width = "35%", left = "55%") %>% 
  # create y axis on grid index 1
  e_y_axis(gridIndex = 1) %>% 
  # create x axis on grid index 1
  e_x_axis(gridIndex = 1) %>% 
  # add tooltip with axis as trigger
  e_tooltip("axis")
```

## Funnel Chart with e_funnel

```{r}
# create funnel data
funnel <- data.frame(
  stage = c("View", "Click", "Purchase"), 
  value = c(80, 30, 20)
)

# from funnel data
funnel %>% 
  # create e-charts object
  e_charts() %>% 
  # add funnel data with value and stage
  e_funnel(value, stage)
```

## Heatmap with e_heatmap

```{r}
# from turnover data
turnover_data %>% 
  # group by position and education level
  group_by(position, education_level) %>%
  # count
  count() %>%
  # ungroup 
  ungroup() %>%
  # create e-chart object with position as x-axis
  e_charts(position) %>% 
  # create heatmap with education level as y-axis and n as z-axis
  e_heatmap(education_level, n) %>% 
  # add visual map
  e_visual_map(n)
```

## Candlestick with e_candle

```{r}
# from amazon data
amazon_data %>%
  mutate(Date = as.character(Date)) %>% 
  # add echart object with Date as x-axis
  e_charts(Date) %>% 
  # add Open, Close, Low, and High value of stock data
  e_candle(opening = Open, closing = Close, low = Low, high = High) %>% 
  # add zoom effect
  e_datazoom(type = "slider") %>% 
  # add title
  e_title("Candlestick chart", "Quantmod data")
```

# River Chart with e_river

```{r}
date_data <- seq.Date(from = as.Date("2020-02-14"), to = as.Date("2020-02-14") + 55, by = "day")

indocovid_data$date <- date_data

indocovid_data %>% 
  e_charts(date) %>% 
  e_river(death_by_day) %>% 
  e_river(in_care_by_day) %>% 
  e_river(new_cases_by_day)
```

# Interactive Maps using Leaflet

## Basic Tiles

```{r}
# call leaflet object
leaflet() %>% 
  # add tiles
  addTiles()
```

## Map Provider

**Stamen Toner**

```{r}
# call leaflet object
leaflet() %>% 
  # add tiles
  addTiles() %>% 
  # using Stamen Toner tile
  addProviderTiles(providers$Stamen.Toner)
```

**CartoDB Positron**

```{r}
# call leaflet object
leaflet() %>% 
  # add tiles
  addTiles() %>% 
  # using CartoDB Positron tile
  addProviderTiles(providers$CartoDB.Positron)
```


**ESRI NatGeoWorld**

```{r}
# call leaflet object
leaflet() %>% 
  # add tiles
  addTiles() %>% 
  # using ESRI NatGeoWorld Map
  addProviderTiles(providers$Esri.NatGeoWorldMap)
```

**Stamen Watercolor**

```{r}
# call leaflet object
leaflet() %>% 
  # add tiles
  addTiles() %>% 
  # using Stamen Watercolor tile
  addProviderTiles(providers$Stamen.Watercolor)
```

```{r}
# call leaflet object
leaflet() %>% 
  # add tiles
  addTiles() %>% 
  # using ESRI NatGeoWorld Map
  addProviderTiles(providers$OpenStreetMap.HOT)
```

## Markers

**Basic Markers**

```{r}
# call leaflet object
leaflet() %>%
  # add tiles
  addTiles() %>%  
  # add marker
  addMarkers(lng=174.768, lat=-36.852)
```

**Circle Markers**

```{r}
# call leaflet object
leaflet() %>%
  # add tiles
  addTiles() %>%  
  # add circle markers with radius
  addCircleMarkers(lng=174.768, lat=-36.852, radius = 100)
```

**Circle**

```{r}
# call leaflet object
leaflet() %>%
  # add tiles
  addTiles() %>%  
  # add circle markers with radius
  addCircles(lng=174.768, lat=-36.852, radius = 100)
```

## Pop-Up and Label

**Pop-Up**

```{r}
# call leaflet object
leaflet() %>%
  # add tiles
  addTiles() %>%  
  # add marker and popup
  addMarkers(lng=174.768, lat=-36.852, popup = "Place where R developed")
```

**Label**

```{r}
# call leaflet object
leaflet() %>%
  # add tiles
  addTiles() %>%  
  # add marker and label
  addMarkers(lng=174.768, lat=-36.852, label = "Place where R developed")
```

## Add Data to Leaflet

**Add Longitude and Latitude**

```{r}
set.seed(1000)

# from geolocation data
geolocation_data %>% 
  # sampling data
  sample_n(size = 100) %>% 
  # call leaflet object
  leaflet() %>% 
  # add tiles
  addTiles() %>% 
  # add markers 
  addMarkers(
    lng = ~longitude,
    lat = ~latitude
  )
```

**Adding Cluster to Maps**

```{r}
set.seed(1000)

# from geolocation data
geolocation_data %>% 
  # sampling data
  sample_n(size = 1000) %>% 
  # call leaflet object
  leaflet() %>% 
  # add tiles
  addTiles() %>% 
  # add markers 
  addMarkers(
    lng = ~longitude,
    lat = ~latitude,
    clusterOptions = markerClusterOptions()
  )
```

**Add Custom Popup**

```{r}
# from quakes data
quakes %>% 
  # call leaflet object
  leaflet() %>% 
  # add tiles
  addTiles() %>% 
  # add markers
  addMarkers(
    lng = ~long,
    lat = ~lat,
    popup = ~paste0("depth: ", depth, ", mag:", mag, ", stations:", stations),
    clusterOptions = markerClusterOptions()
  )
```






